Structural controllability of ecological networks

### 2018-06-19 paper/manuscript.Rmd
Alternative title

---
title: "Working title: Ecological network control"
classoption: a4paper
csl: journal-of-ecology.csl
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
- \usepackage{geometry}
# - \geometry{right=3in,marginparwidth=2.5in}
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{lineno}
- \usepackage{xr}
- \externaldocument[S-]{supp-info}
- \usepackage{siunitx}
- \usepackage{multirow}
- \usepackage{makecell}
- \usepackage{threeparttablex}
documentclass: artikel1
bibliography: phd-bibliography/network-control.bib
---

@@

>>>>

---
title: "Structural controllability of ecological networks"
classoption: a4paper
csl: journal-of-ecology.csl
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
- \usepackage{geometry}
# - \geometry{right=3in,marginparwidth=2.5in}
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{lineno}
- \usepackage{xr}
- \externaldocument[S-]{supp-info}
- \usepackage{siunitx}
- \usepackage{multirow}
- \usepackage{makecell}
- \usepackage{threeparttablex}
documentclass: artikel1
bibliography: phd-bibliography/network-control.bib
---

@@

*Alternative titles:*

* Keystoneness, centrality, and the structural controllability of ecological networks
